Text embedding models reveal high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-01-27 paper/main.tex

Over the past several years, the global pandemic has forced many educators to
teach remotely. This change in world circumstances is happening alongside (and
perhaps accelerating) geometric growth in the availability of high quality
online courses on platforms such as Khan Academy, Coursera, EdX, and others.
Continued expansion of the global internet backbone and improvements in
computing hardware have also facilitated improvements in video streaming,
enabling videos to be easily downloaded and shared by large segments of the
world's population. This exciting time for online course instruction provides
an opportunity to re-evaluate how we, as a global community, educate ourselves
and each other. For example, we can ask: what makes an effective course or
training program? Which aspects of teaching might be optimized or automated?
How and why do learning needs and goals vary across people? How might we lower
barriers to achieving a high quality education?

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real classrooms. In
part, this has led to a recent resurgence of ``naturalistic'' or
``observational'' experimental paradigms that attempt to better reflect more
ethologically valid phenomena that are more directly relevant to real-world
situations and behaviors. In turn, this has brought new challenges in data
analysis and interpretation. A key step towards solving these challenges will
be to build explicit models of real-world scenarios and how people behave in
them (e.g., models of how people learn conceptual content from real-world
courses, as in our current study). A second key step will be to understand
which sorts of signals derived from behaviors and/or other
measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22, MeshEtal20,
PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these models. A third
major step will be to develop and employ reliable ways of evaluating the
complex models and data that are a hallmark of naturalistic paradigms.

>>>>

Over the past several years, the global pandemic has forced many educators to
teach remotely~\citep{MoseEtal21, ShimLee20, KawaEtal21, Whal20}. This change
in world circumstances is happening alongside (and perhaps accelerating)
geometric growth in the availability of high quality online courses on
platforms such as Khan Academy~\citep{Khan04}, Coursera~\citep{Youn12},
EdX~\citep{Kolo13}, and others~\citep{RhoaEtal13}. Continued expansion of the
global internet backbone and improvements in computing hardware have also
facilitated improvements in video streaming, enabling videos to be easily
downloaded and shared by large segments of the world's population. This
exciting time for online course instruction provides an opportunity to
re-evaluate how we, as a global community, educate ourselves and each other.
For example, we can ask: what makes an effective course or training program?
Which aspects of teaching might be optimized or automated? How and why do
learning needs and goals vary across people? How might we lower barriers to
achieving a high quality education?

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real
classrooms~\citep{Kauf03}. In part, this has led to a recent resurgence of
``naturalistic'' or ``observational'' experimental paradigms that attempt to
better reflect more ethologically valid phenomena that are more directly
relevant to real-world situations and behaviors~\citep{NastEtal20}. In turn,
this has brought new challenges in data analysis and interpretation. A key step
towards solving these challenges will be to build explicit models of real-world
scenarios and how people behave in them (e.g., models of how people learn
conceptual content from real-world courses, as in our current study). A second
key step will be to understand which sorts of signals derived from behaviors
and/or other measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22,
MeshEtal20, PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these
models. A third major step will be to develop and employ reliable ways of
evaluating the complex models and data that are a hallmark of naturalistic
paradigms.
